---
title: "p8105_hw5_ph2538"
Author: "Pei Yang Hsieh"
Date: 2018-11-04
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```


## Problem 1

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time


```{r}
#Start with a dataframe containing all file names; the list.files function will help

file_names = 
  data_frame(subID_arm = list.files(path = "./data_1")) %>% 
  mutate(subID_arm = as.character(subID_arm))

#Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

#first write function to read in csv files. Function is named file_name.

read_participant_data <- function(file_name) {
  
 read_csv(paste0("data_1/", file_name)) 

}

#map requires dataset and function

participant_data = map_df(file_names$subID_arm, read_participant_data)

#Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

#file_names_df %>% mutate(study_data = map....) %>% unnest

tidy_participant_data = 
  cbind(file_names, participant_data) %>% 
  janitor::clean_names() %>% 
  mutate(sub_id_arm = str_replace(sub_id_arm, ".csv", "")) %>% 
  separate(sub_id_arm, into = c("arm", "sub_id"), sep = "_") %>% 
  gather(key = week, value = obs, week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", "")) %>% 
  mutate(week = as.numeric(week))

```

### Spaghetti plot

```{r}
#Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

tidy_participant_data %>% 
  ggplot(aes(x = week, y = obs, color = sub_id)) +
  geom_point() +
  geom_line() +
  facet_grid(~arm) + 
  labs(
    title = "Control vs Experimental Arms, Week 1-8",
    x = "Week",
    y = "Observations"
  )

```



The spaghetti plot shows that observations for the experimental arm have much higher values compared to the observations for the control arm. The control arm values consistently remain at low values, while the experimental values have a positive increasing trend.




## Problem 2

### Raw data

```{r}
#Describe the raw data.
homicide_data = read_csv(file = "./data_2/homicide-data.csv")
```


The homicide dataset dimensions are `r dim(homicide_data)`, which means it includes `r nrow(homicide_data)` homicide incidents. Key variables include the incident ID, reported date, victim's first and last name, city and state of incident, and disposition. In addition, it also includes victim's age and race.

### Create city_state variable and summarize

```{r}
#Create a city_state variable (e.g. “Baltimore, MD”)

homicide_data =
  homicide_data %>% 
  mutate(city_state = str_c(city, ", ", state))

#Summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”)

total_homicide =
  homicide_data %>% 
  group_by(city_state) %>% 
  summarize(total = n()) %>% 
  filter(city_state == "Baltimore, MD") 
  
unsolved_homicide =
  homicide_data %>%
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarize(unsolved = n()) %>% 
  filter(city_state == "Baltimore, MD") 

```

### Use prop.test on Baltimore, MD

```{r}
#For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

Baltimore = 
  inner_join(total_homicide, unsolved_homicide, by = "city_state")

Prop_test_baltimore =
  prop.test(Baltimore$unsolved, Baltimore$total) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  knitr::kable(digits = 4)
  
Prop_test_baltimore

```

### Use prop.test on all cities


```{r}
#Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

total_homicide =
  homicide_data %>% 
  group_by(city_state) %>% 
  summarize(total = n())

unsolved_homicide =
  homicide_data %>%
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarize(unsolved = n())

All_cities = 
  inner_join(total_homicide, unsolved_homicide, by = "city_state") 

```

Note that the following prop_test analyses and plot omits the outlier Tulsa, Alabama, which only has 1 homicide.

```{r}
prop_city <- function(unsolved_prop, total_prop) {
  
  prop.test(unsolved_prop, total_prop) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
}

Prop_all_cities =
  All_cities %>% 
  mutate(prop_city = map2(unsolved, total, prop_city)) %>% 
  unnest()

Prop_all_cities
```


### Plot estimates and CI's for all cities

```{r}
#Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

Plot_all_cities =
  Prop_all_cities %>% 
  ggplot(aes(fct_reorder(city_state, estimate), estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Estimates and CIs for All Cities",
    x = "City",
    y = "Estimates"
  )  +
  theme(axis.text.x = element_text(angle = 90)) 

Plot_all_cities
```




