---
title: "p8105_hw5_ph2538"
Author: "Pei Yang Hsieh"
Date: 2018-11-04
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```


## Problem 1

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time


```{r}
#Start with a dataframe containing all file names; the list.files function will help

file_names = 
  data_frame(subID_arm = list.files(path = "./data_1")) %>% 
  mutate(subID_arm = as.character(subID_arm))

#Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

#first write function to read in csv files. Function is named file_name.

read_participant_data <- function(file_name) {
  
 read_csv(paste0("data_1/", file_name)) 

}

#map requires dataset and function

participant_data = map_df(file_names$subID_arm, read_participant_data)

#Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

tidy_participant_data = 
  cbind(file_names, participant_data) %>% 
  janitor::clean_names() %>% 
  mutate(sub_id_arm = str_replace(sub_id_arm, ".csv", "")) %>% 
  separate(sub_id_arm, into = c("arm", "sub_id"), sep = "_") %>% 
  gather(key = week, value = obs, week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", "")) %>% 
  mutate(week = as.numeric(week))

```

### Spaghetti plot

```{r}
#Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

tidy_participant_data %>% 
  ggplot(aes(x = week, y = obs, color = sub_id)) +
  geom_point() +
  geom_line() +
  facet_grid(~arm) + 
  labs(
    title = "Control vs Experimental Arms, Week 1-8",
    x = "Week",
    y = "Observations"
  )

```



The spaghetti plot shows that observations for the experimental arm have much higher values compared to the observations for the control arm. The control arm values consistently remain at low values, while the experimental values have a positive increasing trend.




## Problem 2


```{r}

```

